School accessibility: a new index applied to enrollment and performance inequalities in Sao Paulo

### 2015-09-24 paper.Rmd

---
title: "School accessibility  in Sao Paulo"
title: "School accessibility: a new index with a case study of enrollment and academic performance in Sao Paulo"
author: "Ana Moreno and Robin Lovelace"
date: "Monday, September 21, 2015"
output: pdf_document
---

@@

>>>>

---
title: "School accessibility: a new index applied to enrollment and performance inequalities in Sao Paulo"
author: "Ana Moreno and Robin Lovelace"
date: "`r format(Sys.time(), '%F')`"
output: pdf_document
bibliography: school-access-bib.bib
---

@@

# Introduction

**Contents:**

- Motivations
- General measures of accessibility
- School accessibility

...

The first well-known attempt to define accessibility quantitatively was by @ingram1971concept, which presented a range of measures related to distance (Euclidean and network), barriers and different functions representing distance decay.

This early work made the distinction between accessibility indeces that apply to zones or single 'desire lines':
"relative accessibility is defined as a measure of the effort of overcoming spatial separation between two points, while the integral accessibility is defined as a measure of the effort of overcoming spatial separation between a point and all other points within an area"
[@allen1993accesibility].

# Method: measuring school accessibility

# Results

# Discussion

# Conclusion

# References
